Fixing Lost JavaScript Function Names in Debuggers

### 2011-03-28 trunk/papers/splash-wavefront2011/sigplanconf-template.tex

\begin{table}
\centering
\caption{The total number of functions and the number of named functions in ten famous JavaScript projects.}
\scalebox{0.9}{
  \begin{tabular}{ | l | l | l | l | l |}
  \hline
   Project & Description & Total & Named \\ 
  \hline 
   Closure & Google Web Library & 9195 & 208(2\%) \\ 
  \hline 
   DoJo & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
  \hline 
   ExtJS & JavaScript Framework & 37717 & 1184(3\%) \\ 
  \hline 
   Firebug & Web Development Tool & 3424 & 406(11\%) \\ 
  \hline 
   jQuery & JavaScript Library & 422 & 23(5\%) \\ 
  \hline 
   MochiKit &  JavaScript Library & 1866 & 37(1\%) \\ 
  \hline 
   MooTools & JavaScript Framework & 625 & 7(1\%) \\ 
  \hline 
   Prototype & JavaScript Framework & 645 & 203(31\%) \\ 
  \hline 
   Scriptaculous &  JavaScript Library & 1092 & 208(19\%) \\ 
  \hline 
   YUI &  Yahoo UI Library & 22346 & 922(4\%) \\ 
  \hline 
   All &  & 96008 & 6008(6.3\%) \\ 
  \hline 
  \end{tabular}
  }
 \label{functions} 
\end{table}

@@

A function name must help the developer to
distinguish the function from other functions with different behaviours. The behaviour of a function is dependent to its source code, enclosing scopes (e.g., global and closure variables), the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments. The first two parameters can be almost known from the source code, while the two last parameters are usually not known until the function call at runtime. Therefore, to name a function object, it is enough to name its \textit{function body}.

A function body can be uniquly identified by its location in the source file. A naive proposal for the function name for a function body is a combination of the function file name and line number. Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour. Morover, A proposed function name should be close to the name a developer would choose for the function.

@@

\section{Automated Funcation Naming}

    To tackle the aforementioned issues caused due to the lack of function names, we propose automated function naming by anlyzing the source code and extracting the initial name used for the function object after its creation. To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}.

    We can recognize seven function bodies in the code, none of them has a name. The first function defined in line 9 is called just after its creation and returns another function defined in line 10. The result is assigned to variable {\small\texttt{main}}. Therefore the internal function body is named {\small\texttt{main}} as its corresponding function object is assinged to a variable with this name. What about the outer function itself? We name that
 {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.

\begin{table}
\centering
\caption{Different cases of function object creation and usage in JavaScript.}
\scalebox{0.8}{
\renewcommand\arraystretch{2.0}
\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
  \hline
   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
  \hline

@@

  \end{tabular}
  }
 \label{function-types} 
\end{table}

 The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}. We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}). A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}). However the latter requires knowning the function body of the called function which is not always possible.

    As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are assigned to variable with the same names. Similar to the first two functions which are named {\small\texttt{mainClosure}} and {\small\texttt{main}}, the functions in lines 25 and 27 can be named {\small\texttt{opClosure}} and {\small\texttt{op}} respectively.

\begin{table*}
\centering
\caption{The number of nameless functions in each category defined in table~\ref{function-types}.}
  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l |}
  \hline
     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
  \hline 
   Closure       & 23(0.3\%)  & 0  & 8465(94\%) & 3  & 4  & 0  & 0 & 67(0.7\%)& 16(0.2\%)& 43(0.5\%)& 365(4\%)\\ 
  \hline 
   DOJO          & 9599(61\%) & 6  & 1762(11\%) & 21 & 22 & 2  & 1 & 1143(7\%)& 471(3\%) & 169(1\%) & 2644(17\%) \\ 
  \hline 
   ExtJS         & 30221(83\%)& 0  & 1476(4\%)  & 3  & 16 & 9  & 0 & 820(2\%) & 788(2\%) & 509(1\%) & 2617(7\%) \\ 
  \hline 
   Firebug       & 2296(76\%) & 0  & 539(18\%)  & 1  & 0  & 0  & 0 & 14(0.4\%)& 7(0.2\%) & 6(0.2\%) & 149(5\%) \\ 
  \hline 
   jQuery        & 233(58\%)  & 0  & 34(9\%)    & 0  & 10 & 2  & 0 & 24(6\%)  & 9(2\%)   & 0        & 86(21\%)  \\ 
  \hline 
   MochiKit      & 1080(59\%) & 0  & 383(21\%)  & 0  & 2  & 0  & 0 & 106(6\%) & 18(1\%)  & 41(2\%)  & 181(10\%) \\ 
  \hline 
   MooTools      & 339(55\%)  & 0  & 79(13\%)   & 0  & 4  & 3  & 0 & 53(9\%)  & 21(3\%)  & 14(2\%)  & 105(17\%) \\ 
  \hline 
   Prototype     & 265(60\%)  & 0  & 28(6\%)    & 0  & 0  & 1  & 0 & 25(6\%)  & 44(10\%) & 8(2\%)   & 71(16\%) \\ 
  \hline 
   Scriptaculous & 564(64\%)  & 0  & 75(8\%)    & 0  & 2  & 2  & 0 & 27(3\%)  & 45(5\%)  & 9(1\%)   & 160(18\%) \\ 
  \hline 
   YUI           & 14154(66\%)& 7  & 1721(8\%)  & 0  & 90 & 0  & 0 & 1181(6\%)& 172(1\%) & 95(0.5\%)& 4004(19\%)\\ 
  \hline 
   All           & 58774(65\%)& 23 & 14562(16\%)& 28 & 150& 19 & 1 & 3460(4\%)& 1591(2\%)& 894(1\%) & 10382(12\%) \\ 
  \hline 
  \end{tabular}
 \label{function-types-count} 
\end{table*}

\subsection{Naming Scheme}
We can generalize the approach used for naming functions in the example by studying differnt cases that a function object can be created and used. Once a function object is created, one of the cases presented in Table~\ref{function-types} can happen. One common case of function object creation is by top script named function bodies. We did not considered this case as a separate case as it can be transformed to case 8 where a function body is assigned to a variable. Moreover, Note that functions are created by {\small\texttt{Function}} constructor can be replace by a function body and named in the same way. For every case, we will explain how a name can be assinged to the function.

Names which are specified with a star are reduced from a JavaScript expression. We discuss this reduction in ~\ref{sec:general-element-naming}. Table~\ref{function-types-count} shows the number of nameless functions in each category in the studied projects. These numbers shows how frequent and important a category of functions is in these projects. 
%they have similar pattern

@@

\begin{table}
\centering
\caption{Number of similar, and different function names in comparison to Firebug {\small \texttt{guessFunctionName()}}.}
\scalebox{0.9}{
  \begin{tabular}{ | l | l | l | l | l |}
  \hline
   Project & Similar & Different & UnNamed \\ 
  \hline 
   Closure & 8524(1\%) & 9195 & 516(2\%) \\ 
  \hline 
   DoJo & 12180(1\%) & 9195 & 5780(2\%) \\ 
  \hline 
   ExtJS & 100(1\%) & 9195 & 208(2\%) \\ 
  \hline 
   Firebug & 2901(1\%) & 9195 & 494(0\%) \\ 
  \hline 
   jQuery & 283(1\%) & 9195 & 117(0\%) \\ 
  \hline 
   MochiKit &  1568(1\%) & 9195 & 234(2\%) \\ 
  \hline 
   MooTools & 440(1\%) & 9195 & 128(2\%) \\ 
  \hline 
   Prototype & 292(1\%) & 9195 & 326(0\%) \\ 
  \hline 
   Scriptaculous &  100(1\%) & 9195 & 397(2\%) \\ 
  \hline 
   YUI &  11248(1\%) & 9195 & 3702(2\%) \\ 
  \hline 
   All & 100(1\%) & 9195 & 208(2\%) \\ 
  \hline 
  \end{tabular}
  }
 \label{firebug} 
\end{table}

@@

>>>>

%\section{The Nameless Function Problem}
\section{Anonymous Functions Problem}

\begin{table}
\centering
\scalebox{0.9}{
  \begin{tabular}{ | l | l | l | l | l |}
  \hline
   Project & Description & Total & Named \\ 
  \hline 
   Closure & Google Web Library & 9195 & 208(2\%) \\ 
  \hline 
   DoJo & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
  \hline 
   ExtJS & JavaScript Framework & 37717 & 1184(3\%) \\ 
  \hline 
   Firebug & Web Development Tool & 3424 & 406(11\%) \\ 
  \hline 
   jQuery & JavaScript Library & 422 & 23(5\%) \\ 
  \hline 
   MochiKit &  JavaScript Library & 1866 & 37(1\%) \\ 
  \hline 
   MooTools & JavaScript Framework & 625 & 7(1\%) \\ 
  \hline 
   Prototype & JavaScript Framework & 645 & 203(31\%) \\ 
  \hline 
   Scriptaculous &  JavaScript Library & 1092 & 208(19\%) \\ 
  \hline 
   YUI &  Yahoo UI Library & 22346 & 922(4\%) \\ 
  \hline 
   All &  & 96008 & 6008(6.3\%) \\ 
  \hline 
  \end{tabular}
  }
\caption{The total number of functions and the number of named functions in ten famous JavaScript projects.}
\label{js-functions} 
\end{table}

@@

\section{Discussion}
The anonymous functions problem is discussed in several articles and forums on the web \cite{DisplayName, Zaytsev}. Different solutions have been proposed and discussed by practitioners. A basic solution is a mechanism for naming functions by developers without affecting the variables in scopes. For example, a new property (e.g., \textit{displayName}) in function object can be used for storing the function name, or the function name can be defined by annotation. Although these solutions may help, they cause developers extra work.

%Morover, these solutions do not work for lagacy code.
We instead propose an automated approach for naming all functions by anlyzing the source code. Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.

%\subsection{Rationale}
\subsection{Function Object vs. Function Body}%What Should be Named?}
The first question arises is that which one should be named? the function body or the function object. A function name must help the developer to distinguish the function from other functions with different behaviours. The behaviour of a function object, in addition to its body (the source code), is dependent to the enclosing scopes (e.g., global and closure variables). Although the actual enclosing scopes are not known until the function object creation, their structure can be almost known from the enclosing source code. Therefore, to name a function object, it is fair enough to name its \textit{function body}.

%\subsubsection{Static vs. Dynamic}
%Can we improve the names at runtime?
% function object path in dom model is good candidate for the name but only for persistent objects ?

%\subsubsection{Local vs. Global}

%It is conceivable that two function objects which are created from the same function body have different enclosing scopes and therefore different behaviours.

%, the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments. The first two parameters can be almost known from the source code and are less dependent to the runtime while the last two parameters are usually not known until the function call at runtime.

%\subsubsection{Is it possible to automatically name all functions?}
\subsection{What Makes a Good Function Name?}
A function name should be useful for both the developer who are familar with the code and the developer who is not. It should explains the function behaviour, or an abstraction of the function behaviour, or why/where the function is used (e.g., to create object \textit{foo}), or at least works as an identifier.

A function body can be uniquely identified by its location in the source file. A naive proposal for the function name for a function body is a combination of the function file name and line number. Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour. On the other extreme extend, the function body itself can be used as the function identifier. This identifier it too long to be displayed and read by the developer.

@@

%\subsubsection{Other Challenges}%
% functions pass the name as string, different types of class definitions

\section{Automated Funcation Naming}
%	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code. Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.

\begin{table}
\centering
\scalebox{0.8}{
\renewcommand\arraystretch{2.0}
\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
  \hline
   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
  \hline

@@

  \end{tabular}
  }
\caption{Different cases of function object creation and usage in JavaScript.}
\label{table:function-types} 
\end{table}

\begin{table*}
\centering
  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l |}
  \hline
     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
  \hline 
   Closure       & 23(0.3\%)  & 0  & 8465(94\%) & 3  & 4  & 0  & 0 & 67(0.7\%)& 16(0.2\%)& 43(0.5\%)& 365(4\%)\\ 
  \hline 
   DOJO          & 9599(61\%) & 6  & 1762(11\%) & 21 & 22 & 2  & 1 & 1143(7\%)& 471(3\%) & 169(1\%) & 2644(17\%) \\ 
  \hline 
   ExtJS         & 30221(83\%)& 0  & 1476(4\%)  & 3  & 16 & 9  & 0 & 820(2\%) & 788(2\%) & 509(1\%) & 2617(7\%) \\ 
  \hline 
   Firebug       & 2296(76\%) & 0  & 539(18\%)  & 1  & 0  & 0  & 0 & 14(0.4\%)& 7(0.2\%) & 6(0.2\%) & 149(5\%) \\ 
  \hline 
   jQuery        & 233(58\%)  & 0  & 34(9\%)    & 0  & 10 & 2  & 0 & 24(6\%)  & 9(2\%)   & 0        & 86(21\%)  \\ 
  \hline 
   MochiKit      & 1080(59\%) & 0  & 383(21\%)  & 0  & 2  & 0  & 0 & 106(6\%) & 18(1\%)  & 41(2\%)  & 181(10\%) \\ 
  \hline 
   MooTools      & 339(55\%)  & 0  & 79(13\%)   & 0  & 4  & 3  & 0 & 53(9\%)  & 21(3\%)  & 14(2\%)  & 105(17\%) \\ 
  \hline 
   Prototype     & 265(60\%)  & 0  & 28(6\%)    & 0  & 0  & 1  & 0 & 25(6\%)  & 44(10\%) & 8(2\%)   & 71(16\%) \\ 
  \hline 
   Scriptaculous & 564(64\%)  & 0  & 75(8\%)    & 0  & 2  & 2  & 0 & 27(3\%)  & 45(5\%)  & 9(1\%)   & 160(18\%) \\ 
  \hline 
   YUI           & 14154(66\%)& 7  & 1721(8\%)  & 0  & 90 & 0  & 0 & 1181(6\%)& 172(1\%) & 95(0.5\%)& 4004(19\%)\\ 
  \hline 
   All           & 58774(65\%)& 23 & 14562(16\%)& 28 & 150& 19 & 1 & 3460(4\%)& 1591(2\%)& 894(1\%) & 10382(12\%) \\ 
  \hline 
  \end{tabular}
\caption{The number of nameless functions in each category defined in table~\ref{table:function-types}.}
\label{function-type-count} 
\end{table*}

\subsection{basic idea}
   Developers refer to function objects in JavaScript in different ways. For permanet global functions (e.g., classes, utility functions) the alias used to access the function object is the natural way of refereing. Other function objects which have shorter life time and are not assigned to an alias, are usually refered by their role or the way they affect other objects. We employ this fact and name function objects using their aliases or the aliases of objects they affect.

      On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created. Therefore, we analyze the code to find all names that the function object is assigned to them. For cases where the function object is not assigned to a variable or object property but is used to produce other values we keep track of the function effect on other identifiers.

   To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name. For every function we first build a summary. The summary explains how the function object is used in relation to other identifiers. The first function defined in line 9 is called just after its creation and returns another function defined in line 10. The result is assigned to variable {\small\texttt{main}}. In this case the summary for the first function is {\small\texttt{main<}} as it produces the {\small\texttt{main}} object. The second function is directly assigned to {\small\texttt{main}} and thus its name will be {\small\texttt{main}}.

%    Therefore the internal function body is named {\small\texttt{main<}} as its corresponding function object is assinged to a variable with this name. What about the outer function itself? We name that {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.

The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}. This function contributes in producing the {\small\texttt{result}} value. Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
%We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}). A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}). However the latter requires knowning the function body of the called function which is not always possible.

As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names. The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.

%Similar to the first two functions which are named {\small\texttt{mainClosure}} and {\small\texttt{main}},

\subsection{Function Object Creation and Consumption}
%     and extracting the initial name used for the function object after its creation. 
%In the third subsection we discuss qualities we expect from an automatically created function name.

\subsection{Naming Scheme}
We can generalize the approach used for naming functions in the example by studying differnt cases that a function object can be created and used. Once a function object is created, one of the cases presented in Table~\ref{table:function-types} can happen. One common case of function object creation is by top script named function bodies. We did not considered this case as a separate case as it can be transformed to case 8 where a function body is assigned to a variable. Moreover, Note that functions are created by {\small\texttt{Function}} constructor can be replace by a function body and named in the same way. For every case, we will explain how a name can be assinged to the function.

Names which are specified with a star are reduced from a JavaScript expression. We discuss this reduction in ~\ref{sec:general-element-naming}. Table~\ref{function-type-count} shows the number of nameless functions in each category in the studied projects. These numbers shows how frequent and important a category of functions is in these projects. 
%they have similar pattern

@@

\begin{table}
\centering
\scalebox{0.9}{
  \begin{tabular}{ | l | l | l | l | l |}
  \hline
   Project & Similar & Different & UnNamed \\ 
  \hline 
   Closure & 8524(1\%) & 9195 & 516(2\%) \\ 
  \hline 
   DoJo & 12180(1\%) & 9195 & 5780(2\%) \\ 
  \hline 
   ExtJS & 100(1\%) & 9195 & 208(2\%) \\ 
  \hline 
   Firebug & 2901(1\%) & 9195 & 494(0\%) \\ 
  \hline 
   jQuery & 283(1\%) & 9195 & 117(0\%) \\ 
  \hline 
   MochiKit &  1568(1\%) & 9195 & 234(2\%) \\ 
  \hline 
   MooTools & 440(1\%) & 9195 & 128(2\%) \\ 
  \hline 
   Prototype & 292(1\%) & 9195 & 326(0\%) \\ 
  \hline 
   Scriptaculous &  100(1\%) & 9195 & 397(2\%) \\ 
  \hline 
   YUI &  11248(1\%) & 9195 & 3702(2\%) \\ 
  \hline 
   All & 100(1\%) & 9195 & 208(2\%) \\ 
  \hline 
  \end{tabular}
  }
 \label{firebug} 
\caption{Number of similar, and different function names in comparison to Firebug {\small \texttt{guessFunctionName()}}.}
\end{table}

@@

\bibitem{DisplayName}
Add prettyName/displayName support to Profiler output and Stacks.
\newblock \emph{Firebug Bug Repository},
\newblock http://code.google.com/p/fbug/issues/detail?id=1811
